% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\graphicspath{ {./images/} }

% Please include a clear, concise, and descriptive title
\title{CPD Report} 

% Please do not change the subtitle
\subtitle{COMP330 CPD Report}

% Please put your student number in the author field
\author{1507516}

\begin{document}

\maketitle


\section{Career Goals}
In this final semester I have encountered a lot of new challenges compared to previous years, especially emotional and mental problems due to the pressure of final year, and the effect this semesters grade has on my life.
My career goals for after university are to start seeking employment within the games industry, whether that be indie or AAA. If that fails, I may start looking for an IT tech job just to get some work experience, as they seem to be more common.

\section{Summary of Key Challenges}


%%%% Challenge 1 - the affective domain, such as your ability to identify and manage different mental states and emotions
%Feeling like I am not intelligent enough to understand the concepts behind something, and am unable to
\subsection{Not Feeling Intelligent Enough to Carry out Complex Programming Tasks}
% Justification and importance
Throughout this semester I spent a lot of time working on tasks that I thought I was not intelligent enough to learn, just because there was a very steep learning curve associated to some of the projects I have been working on this semester.
Learning how to approach new complex tasks is important because in this industry, new complex software is being developed all the time, so being able to feel confident enough to start learning is an important skill.
\par

% How the issue affects my work
This issue effected both my dissertation and group game project, for my dissertation, there are a lot of very complex terms and AI techniques that I felt overwhelmed by.

\par

% SMART Plan to avoid this in the future
I know that this issue is less to do with my intelligence and more to do with my attitude to learning, as I know if I put the time into learning something, I can do it.

When I was researching how to overcome this issue, I found a reddit post that many people in the comments stated that the best way to grasp concepts is to be exposed to them multiple times with space between them \cite{Reddit}.

So over this summer I will start researching more complex topics that I have felt to be too unintelligent for, such as design patterns, and complex C++ OOP designs, then sit down and read about these topics at least once a week so their concepts will eventually sink in, by the end of summer, I will reflect on my progress towards these topics by viewing my new coding styles for my game project that I am working on.



%%%% Challenge 2 - the interpersonal domain, such as your ability to communicate and organise activity with peers
% Ingaging in discussions more, instead of just listening
\subsection{Engaging more  in group discussions}

% Justification and importance
At my time in college and university I have always been more of a listener than a talker, and I often find it hard to engage in group discussions. This effects my learning because being able to engage in group discussions can lead to new ideas and perspectives, as well as being able to solve more complex problems that I would not be able to sole on my own.

% How the issue affects my work
Discussing complex dissertation topics, such as statistical analysis and the use of R within my year group could have given me better insights and understanding towards these complex topics.
\par




% SMART Plan to avoid this in the future
When researching methods to overcome these issues, one source \cite{Group} suggests to use a methods of conversation that gathers viewpoints from everyone in the group by using "Circle stories".






%%%% Challenge 3 - the dispositional domain, such as your ability to manage time and remain disciplined
% Stopping working for the day because I got something done.
\subsection{Stopping a task because I think I have done enough for one day}

% Justification and importance
Throughout this year, when there are no looming deadlines, I tend to stop working on my uni work when I feel I have accomplished something, no matter how small.

% How the issue affects my work
This generally effects my work as when I get something done, it disrupts the flow of my work and takes a lot longer to finish a task. Moreover, it also means I tend to leave more work to do nearer the project deadline.

% SMART Plan to avoid this in the future
To overcome this it depends on what type of job I get after university, if I get a 9-5 job, then this will solve that problem, because I will not have the temptation to leave early. However if I get a freelance job etc, the motivation of getting paid should be enough to motivate me to spend more time working on the project.
\par



%%%% Challenge 4 - the cognitive domain, such as your knowledge of programming languages or frameworks
% using python at the end of this semester
\subsection{Becoming Familiar With Other Game Engines}
% Justification and importance
Since being at Falmouth, I have only learnt how to use the Unity game engine, I have not even tried the Unreal Engine or lumberyard etc. This will limit my employability after university, as many games companies will be using some of the other big game engines.

% How the issue affects my work
I have seen a lot of very good looking games that have been developed using the unreal engine, and I would like to gather some experience with these engines before applying for jobs, as it is one more thing that I can put on my CV.

% SMART Plan to avoid this in the future
There was talk amongst the other third year BSc students to work on a project together over the summer, as well as doing some game jams. This will be done using the Unreal Engine, as most of the year group is familiar with it, apart from me. So over the first few weeks after all the deadlines are handeded in, I will download and create a small game in the Unreal Engine, as well as participate in some game jams with the other 3rd years.
\par




%%%% Challenge 5 - the procedural domain, such as your abilities to apply computing concepts and problem solving skills
%
\subsection{Prioritising Tasks}

% Justification and importance
In this semester I spent quite a lot of time working on things that never actually lead anywhere, for instance in the group game I worked on a few various features that never got implemented, and in the dissertation I was working on the visualization stuff, that had no relation to the final product.

% How the issue affects my work
This meant that I essentially wasted all that time, even though I thought I was being productive.

\par


% SMART Plan to avoid this in the future
To avoid this in the future, over the summer when creating user stories, I will have a priority label on each user story, this will help make sure I spent time working on the items that need to be worked on, rather than items that I would prefer to work on, that may not actually end up being implemented.


\section{Conclusion}
These are my main weaknesses I faced this year, which I should address before getting an industry job, so I don't take them with me to my career in the software industry.


%%% OTHER
% Getting used to GVG-AI framework
%

\bibliographystyle{ieeetr}
\bibliography{comp340-Reflective-Report}


\end{document}
