% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\graphicspath{ {./images/} }

% Please include a clear, concise, and descriptive title
\title{Reflective Report} 

% Please do not change the subtitle
\subtitle{COMP240 Reflective Report}

% Please put your student number in the author field
\author{1507516}

\begin{document}

\maketitle


\section{Career Goals}
Over the course of this year I have learned a lot of new skills, but I do feel more confident that I would like to pursue the career of game developer.
This report will cover the main issues I struggled with over this year.
%SMART actions to resolve these issues


\section{Summary of Experiances}
%More reading of papers and books.
\subsection{Reading the necessary literature before solving a complex programming problem}
I found my self a few times this year trying to tackle a problem such as networking or AI and finding that if I had read the necessary literature about the topic I was working on before hand, I would of found it far easier. For example when I was writing the research journals for the AI project I was doing a lot of reading in parallel to the writing, and I found a few clever solutions to a few of my problems in some of the academic literature. However for the networking module a few of the papers I read made the networking module a lot easier to understand what was going on.
To try and overcome this issue I will finish reading the books and academic literature I started this year over summer. I will also find some material about legacy systems and the other projects so I am more prepared for next year.

%Learning new game engine.
%Procedural domain
\subsection{Managing tasks}
When managing tasks over the course of this year, I have primarily been using trello to keep track of the progress of the projects. However in almost all of my trello boards I have not followed the mountain goat user stories style. I'm pretty sure most of my trello boards contain some cards that are just tasks. I have found it hard to create cards that are not tasks. What I have found over the course of this semester is most of the time that I create a trello card is when I have either started working on something new or I have already done the task. This is not the proper way in which trello is suppose to be used.
In order to overcome this next year I will attempt to fully flesh out the trello baord at the beginning of the project instead of while I'm working on the project and get into the rythm of picking a card to work on each day. Further more this will help with my even distribution of workload issue if I try and complete one trello card per day for each project.

%Even distribution of workload / not getting caught up in a project I like.
%Dispositional domain
\subsection{Even Distribution of workload}
This has been a common issue for most of my life, and is going to be a hard issue to overcome. There are some projects that I really click with and will spend weeks on, and neglect other projects. This may be fine in game development, but in academia this means I will get a overall worse grade because the neglected projects will bring my grade down significantly.
In my weekly reports I have tried a few things to overcome this issue, but with no luck so far. However I have come up with an idea, because I sill am not too sure what I am going to do for my dissertation, over summer I will work on a game that covers most the disciplines that have been covered in the course so far, e.g. AI, PCG etc.. I will aim to work out what I enjoy the most and harness this flaw into a strength to work harder for my dissertation project.

%Not digging myself a hole in group projects / group project communication /Wokring with a large team
%Mental states and emotions (Active domain)
\subsection{Collaboration}
When working with another team that you have very little communication with can create lots of issues. One of the issues that I found myself having was having a negative feedback loop when I went a long time with no communication. I would feel bad for not helping the BA team or popping in to see how they were doing in the second semester, but I also didn't want to because I felt bad for not helping them as much as I should of. Furthermore their team had no attempt to contact me and see how the work I was doing was going.
To overcome this issue next year I will attempt to follow the agile philosophy more closely, this means perform stand up meetings and keep up to date about what others are currently working on. 

%Code
%Cognative Domain
\subsection{Writing reusable code}
Over the course I have written a lot of C++ code, and each time I write a bit of code I only think about how that bit of code can be used to solve that particular problem. So I will often use some functions that are only appropriate to that project, this means that when I start a new project I have to write \textit{similar} code to solve pretty much the same problem. This can be avoided if I can make some of my functions and classes more general so that other values can be passed in instead. An example of where I did this was in my AI project, the agentManager class I wrote to control the agents had to be re-written for when I copied the code into the networking project.
To attempt to overcome this issue, over the summer I will aim to refactor some of my existing non-reusable code into something that can be ported to other projects. E.g. A batch renderer in SDL that will render sprites that are set in different layers. This will help me understand the principles of how to make more reusable code.


\end{document}
